SRG operator evolution

### 2019-05-31 Notes/SRG_operator_evolution/srg_operator_evolution.tex
Updates to SRG operator evolution notes.
Added captions to figures.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% File: srg_operator_evolution.tex
%
% Author: A. J. Tropiano (tropiano.4@osu.edu)
% Date: May 20, 2019
%
% Notes on SRG operator evolution project.
%
% Revision history:
% 	May 30, 2019 - Renamed srg_operator_evolution.tex from operator_evolution_May20.tex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn10_3S1_Block-diag3,00}%
	}
	\caption{Caption.}
	\label{momentum_projection_contours_q3,00_kvnn10}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q0,30_kvnn10_3S1_Wegner}
	\caption{Caption.}
	\label{momentum_projection_contours_q0,30_kvnn10}
\end{figure}

\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{deuteron_momentum_distribution_kvnn10_Wegner_lamb1,5}%
	}
	\quad
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{deuteron_momentum_distribution_kvnn10_Block-diag2,00_lamb1,5}%
	}
	\quad
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{deuteron_momentum_distribution_kvnn10_Block-diag3,00_lamb1,5}%
	}
	\caption{Caption.}
	\label{deuteron_momentum_distribution_kvnn10}
\end{figure}

\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn10_Wegner_lamb1,5}%
	}
	\quad
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn10_Block-diag2,00_lamb1,5}%
	}
	\quad
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn10_Block-diag3,00_lamb1,5}%
	}
	\caption{Caption.}
	\label{continuum_state_momentum_distribution_eps200,0_kvnn10}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn106_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{momentum_projection_contours_q3,00_kvnn106}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn107_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{momentum_projection_contours_q3,00_kvnn107}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn111_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{momentum_projection_contours_q3,00_kvnn111}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn112_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{momentum_projection_contours_q3,00_kvnn112}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn222_3S1_Block-diag3,00}%
	}
	\caption{Caption.}
	\label{momentum_projection_contours_q3,00_kvnn222}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn224_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{momentum_projection_contours_q3,00_kvnn224}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% File: srg_operator_evolution.tex
%
% Author: A. J. Tropiano (tropiano.4@osu.edu)
% Date: May 20, 2019
%
% Notes on SRG operator evolution project.
%
% Revision history:
% 	May 31, 2019 - Renamed to srg_operator_evolution.tex from operator_evolution_May20.tex. Added a description of computing SRG unitary
%                              transformations. Added momentum projection operator contours and momentum distribution plots.                            
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn10_3S1_Block-diag3,00}%
	}
	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Entem-Machleidt N$^3$LO non-local potential with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c). Here $q=3$ fm$^{-1}$.}
	\label{momentum_projection_contours_q3,00_kvnn10}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q0,30_kvnn10_3S1_Wegner}
	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Entem-Machleidt N$^3$LO non-local potential with the Wegner generator. Here $q=0.3$ fm$^{-1}$.}
	\label{momentum_projection_contours_q0,30_kvnn10}
\end{figure}

\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{deuteron_momentum_distribution_kvnn10_Wegner_lamb1,5}%
	}
	\quad
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{deuteron_momentum_distribution_kvnn10_Block-diag2,00_lamb1,5}%
	}
	\quad
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{deuteron_momentum_distribution_kvnn10_Block-diag3,00_lamb1,5}%
	}
	\caption{Momentum probability densities of the deuteron SRG-evolving the wave function to $\lambda=1.5$ fm$^{-1}$ from the Entem-Machleidt N$^3$LO non-local potential with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c). The black dotted line corresponds to the momentum probability density of the initial deuteron wave function.}
	\label{deuteron_momentum_distribution_kvnn10}
\end{figure}

\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn10_Wegner_lamb1,5}%
	}
	\quad
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn10_Block-diag2,00_lamb1,5}%
	}
	\quad
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn10_Block-diag3,00_lamb1,5}%
	}
	\caption{Momentum probability densities of the continuum state at $\epsilon \approx 200$ MeV SRG-evolving the wave function to $\lambda=1.5$ fm$^{-1}$ from the Entem-Machleidt N$^3$LO non-local potential with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c). The black dotted line corresponds to the initial momentum probability density.}
	\label{continuum_state_momentum_distribution_eps200,0_kvnn10}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn106_3S1_Block-diag2,00}%
	}
	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the RKE N$^3$LO semi-local potential with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b). Here $q=3$ fm$^{-1}$ and the EFT cutoff is $450$ MeV.}
	\label{momentum_projection_contours_q3,00_kvnn106}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn107_3S1_Block-diag2,00}%
	}
	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the RKE N$^3$LO semi-local potential with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b). Here $q=3$ fm$^{-1}$ and the EFT cutoff is $500$ MeV.}
	\label{momentum_projection_contours_q3,00_kvnn107}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn111_3S1_Block-diag2,00}%
	}
	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the RKE N$^4$LO semi-local potential with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b). Here $q=3$ fm$^{-1}$ and the EFT cutoff is $450$ MeV.}
	\label{momentum_projection_contours_q3,00_kvnn111}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn112_3S1_Block-diag2,00}%
	}
	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the RKE N$^4$LO semi-local potential with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b). Here $q=3$ fm$^{-1}$ and the EFT cutoff is $500$ MeV.}
	\label{momentum_projection_contours_q3,00_kvnn112}
\end{figure}

\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn111_Wegner_lamb1,5}%
	}
	\quad
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn111_Block-diag2,00_lamb1,5}%
	}
	\quad
	\subfloat[]{%
	\includegraphics[clip,width=0.3\columnwidth]{continuum_state_momentum_distribution_eps200,0_kvnn111_Block-diag3,00_lamb1,5}%
	}
	\caption{Momentum probability densities of the continuum state at $\epsilon \approx 200$ MeV SRG-evolving the wave function to $\lambda=1.5$ fm$^{-1}$ from the RKE N$^4$LO semi-local potential with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c). The black dotted line corresponds to the initial momentum probability density. Here the EFT cutoff is $450$ MeV.}
	\label{continuum_state_momentum_distribution_eps200,0_kvnn111}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn222_3S1_Block-diag3,00}%
	}
	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Gezerlis et al. N$^2$LO local potential with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c). Here $q=3$ fm$^{-1}$ and the EFT cutoff is $1$ fm.}
	\label{momentum_projection_contours_q3,00_kvnn222}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn224_3S1_Block-diag2,00}%
	}
	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Gezerlis et al. N$^2$LO local potential with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b). Here $q=3$ fm$^{-1}$ and the EFT cutoff is $1.2$ fm.}
	\label{momentum_projection_contours_q3,00_kvnn224}
\end{figure}
